---
title: "HW9 Q2"
output: html_document
---

```{r setup, include=FALSE}

library(ggplot2)
library(magrittr)

knitr::opts_chunk$set(echo = TRUE)
```

## Q2 Regression Coefficients are Random Variables

Given:

```{r a new enigma}
rmystery <- function(n){
  x = runif(n)
  y = runif(n, min=0, max = 1/x)
  data.frame(x=x,y=y)
}

data <- rmystery(100)

data %>%
  ggplot()+
  aes(x=x,y=y)+
  geom_point()+
  scale_x_continuous(limits = c(0, 1.1)) +
  scale_y_continuous(limits = c(0, 8))

```

### Q2.1 Set up an "experiment" for \`rmystery\`

Create a function, called `experiment_m`, which draws 100 datapoints from the mystery distribution above, fits a regression of y on x, then returns the slope coefficient.

Run your function a few times and notice that you get different values for the slope each time. Remind yourself that to a statistician, slope coefficients are random variables. We always pretend that data comes from a joint distribution, so if we could magically rewind time and get
new data, we'd get new slope coefficients.

Use the visualization trick to approximate the sampling distribution of the slope. Run your experiment function 1000 times and plot a histogram of your result. What do you notice about the sampling distribution?

```{r}
experiment_m <- function() {
data <- rmystery(100)
model <- lm(y~x,data=data)
model$coefficients[2] #slope coefficient
}

Beta1 <- replicate(1000,experiment_m())
Beta1_hist <- data.frame(z=Beta1)
Beta1_hist %>%  
  ggplot() + 
  aes(z) +
  geom_histogram(fill = "red", color = "white", bins = 50) +
  ggtitle("Histogram of slope for Q2.1 rmystery")+
  labs(x = "N", y="Count")

```

Left Skew

### Q2.2 Explain your results for \`rmystery\`

If the sampling distribution is normal, explain why. If it is not normal, explain why. Limit your response to 5 sentences. (Hint: think about the large sample assumptions.)

[Not DONE]{style="color:red"}

### Q2.3 A New Enigma

Given:

```{r}
renigma <- function(n){
  x = runif(n)
  y = runif(n, min=0, max = (1-x)^2)
  data.frame(x=x,y=y)
}
plot(renigma(100))

```

Create a function, called `experiment_e`, which draws 100 datapoints from the enigma distribution above, fits a regression of y on x, then returns the slope coefficient.

Run your experiment function 1000 times and plot a
histogram of your result. What do you notice about the sampling

```{r}

experiment_m <- function() {
data <- renigma(100)
model <- lm(y~x,data=data)
model$coefficients[2] #slope coefficient
}

Beta1 <- replicate(1000,experiment_m())
Beta1_hist <- data.frame(z=Beta1)
Beta1_hist %>%  
  ggplot() + 
  aes(z) +
  geom_histogram(fill = "red", color = "white", bins = 50) +
  ggtitle("Histogram of slope for Q2.1 rmystery")+
  labs(x = "N", y="Count")

```

Normal

### Q2.4 Explain your results for \`renigma\`

If the sampling distribution is normal, explain why. If it is not normal, explain why. Limit your response to 5 sentences. (Hint: think about the large sample assumptions)

[Not Done]{style="color:red"}
