---
title: "HW9"
output: html_document
---

```{r setup, include=FALSE}
## install the package if it's not installed
## note: need to install libgit2-dev in terminal
##      >> apt-get update
##      >> apt-get install libgit2-dev
install.packages("remotes")
remotes::install_github("baumer-lab/fec16",force=TRUE)
# then select 1 for all updates
library(fec16)

library(ggplot2)
library(magrittr)
install.packages("gridExtra")
library(gridExtra)

install.packages('dplyr')
library(dplyr)

knitr::opts_chunk$set(echo = TRUE)
```

## Q3.1 - Exploring - Make Histograms

```{r}
percent_hist <- data.frame(z=results_house$general_percent)
h1 <- percent_hist %>%  
  ggplot() + 
  aes(z) +
  geom_histogram(fill = "red", color = "white", bins = 50) +
  ggtitle("Histogram of Q3.1 Exploring Votes")+
  labs(x = "Percentage of Votes by Campaign", y="Count")

ttl <- data.frame(z=campaigns$ttl_disb)
h2 <- ttl %>%  
  ggplot() + 
  aes(z) +
  geom_histogram(fill = "red", color = "white", bins = 50) +
  ggtitle("Histogram of Q3.1 Exploring Spending")+
  labs(x = "Spending By Campaign($)", y="Count")+  
  scale_x_continuous(limits = c(0,100e3))+
  scale_y_continuous(limits = c(0,100))

combined_plots <- grid.arrange(h1, h2, ncol = 2)
#rm(h1,h2,combined_plots)
```

first, roughly symmetric. second, right skew

### Q3.2 Exploring - Build a Data Frame pt 1

Create a new dataframe by joining `results_house` and `campaigns` using the `inner_join` function from `dplyr` on the field `cand_id`.

### Q3.3 Exploring - Build a Data Frame pt 2

Create a new dataframe by joining `results_house` and `campaigns` using the `inner_join` function from `dplyr` on the field `cand_id`.

```{r}

# Inner join based on the "test" column
result <- inner_join(results_house, campaigns, by = "cand_id")

# Print the result
dim(result)

```
