---
title: "HW9"
output: html_document
---

```{r setup, include=FALSE}
## install the package if it's not installed
## note: need to install libgit2-dev in terminal
##      >> apt-get update
##      >> apt-get install libgit2-dev
install.packages("remotes")
remotes::install_github("baumer-lab/fec16",force=TRUE)
# then select 1 for all updates
library(fec16)

library(ggplot2)
library(magrittr)
install.packages("gridExtra")
library(gridExtra)

install.packages('dplyr')
library(dplyr)

knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

**Given**

L = 11.5 + 2w + 1.5c - 1.2o

L = $\beta_0$ + $\beta_1$w + $\beta_2$c + $\beta_3$h

**Putting into a system of equations:**

Solving for L where c = 1

15 = $\beta_0$ + $\beta_1$w + $\beta_2$c + 0

Solving for L where h = 1

13.5 = $\beta_0$ + $\beta_1$w + 0 + $\beta_3$h

Solving for L where o = 1

12.3 = $\beta_0$ + $\beta_1$w + 0 + 0

**Creating a matrix** form ax=b where x is the beta values

a =

```{=latex}
$
\begin{bmatrix}
1 & 1 & 0\\
1 & 0 & 1\\
1 & 0 & 0
\end{bmatrix}
$
```
x =

```{=tex}
\begin{bmatrix}
\beta_0 + \beta_1 w\\
\beta_2\\
\beta_3
\end{bmatrix}
```
b = x =

```{=tex}
\begin{bmatrix}
15\\
13.5\\
12.3
\end{bmatrix}
```
See below for solver

```{r}

install.packages('matlib')
library(matlib) 
w = 1

lifespan_orig <- function(animal){
  c = 0
  h = 0
  o = 0
  w = 1
  if (animal == "c") {
    c=1
  }
  else if (animal == "h") {
    h=1
  }
  else if (animal == "o") {
    o=1
  }
  L = 11.5+2*w+1.5*c-1.2*o
}

#Solved with w=1
L_o = lifespan_orig("o")
L_h = lifespan_orig("h")
L_c = lifespan_orig("c")


L_new  = B0  + B1 * w +  B2 * c +   0 * o + B3 * h

# Solving for different versions of L_new...
# B_0 is 10.3, B_1 is 2,  L_orig = 11.5 - 1.2
L_new (o=1) = 10.3 + 2 * w + 2.7 * 0 + 0 * 1 + 1.2 * 0    

# B_3 is 1.2, L_orig = 11.5
L_new (h=1) = 10.3 + 2 * w + 2.7 * 0 + 0 * 0 + 1.2 * 1 # o = 0, c = 0

# B_2 is 2.7.  L_orig = 11.5 + 1.5
L_new (c=1) = 10.3 + 2 * w + 2.7 * 1 + 0 * 0 + 1.2 * 0 # o = 0, h = 0
```

```{r cars}
rmystery <- function(n){
  x = runif(n)
  y = runif(n, min=0, max = 1/x)
  data.frame(x=x,y=y)
}
#plot(rmystery(100))

data <- rmystery(100)

plt <- data %>%
  ggplot()+
  aes(x=x,y=y)+
  geom_point()+
  scale_x_continuous(limits = c(0, 1.1)) +
  scale_y_continuous(limits = c(0, 8))
plt
```

## Including Plots

You can also embed plots, for example:

```{r}
# draw 100 datapoints from the mystery distribution above, fits a regression of y on x, then returns the slope coefficient.

# Run your experiment function 1000 times and plot a histogram of your result

experiment <- function() {
data <- rmystery(100)
model <- lm(y~x,data=data)
model$coefficients[2] #slope coefficient
}

Beta1 <- replicate(1000,experiment())
Beta1_hist <- data.frame(z=Beta1)
h <- Beta1_hist %>%  
  ggplot() + 
  aes(z) +
  geom_histogram(fill = "red", color = "white", bins = 50) +
  ggtitle("Histogram of slope for Q2.1 rmystery")+
  labs(x = "N", y="Count")+
  scale_x_continuous(limits = c(-50,0))+
  scale_y_continuous(limits = c(0,100))
h
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r}
renigma <- function(n){
  x = runif(n)
  y = runif(n, min=0, max = (1-x)^2)
  data.frame(x=x,y=y)
}
plot(renigma(100))

```

```{r}
# draw 100 datapoints from the mystery distribution above, fits a regression of y on x, then returns the slope coefficient.

# Run your experiment function 1000 times and plot a histogram of your result

experiment_m <- function() {
data <- renigma(100)
model <- lm(y~x,data=data)
model$coefficients[2] #slope coefficient
}

Beta1 <- replicate(1000,experiment_m())
Beta1_hist <- data.frame(z=Beta1)
h <- Beta1_hist %>%  
  ggplot() + 
  aes(z) +
  geom_histogram(fill = "red", color = "white", bins = 50) +
  ggtitle("Histogram of slope for Q2.1 rmystery")+
  labs(x = "N", y="Count")
h

```

## Q3.1 - Exploring - Make Histograms

```{r}
percent_hist <- data.frame(z=results_house$general_percent)
h1 <- percent_hist %>%  
  ggplot() + 
  aes(z) +
  geom_histogram(fill = "red", color = "white", bins = 50) +
  ggtitle("Histogram of Q3.1 Exploring Votes")+
  labs(x = "Percentage of Votes by Campaign", y="Count")

ttl <- data.frame(z=campaigns$ttl_disb)
h2 <- ttl %>%  
  ggplot() + 
  aes(z) +
  geom_histogram(fill = "red", color = "white", bins = 50) +
  ggtitle("Histogram of Q3.1 Exploring Spending")+
  labs(x = "Spending By Campaign($)", y="Count")+  
  scale_x_continuous(limits = c(0,100e3))+
  scale_y_continuous(limits = c(0,100))

combined_plots <- grid.arrange(h1, h2, ncol = 2)
```

first, roughly symmetric. second, right skew

```{r}

# Inner join based on the "test" column
result <- inner_join(results_house, campaigns, by = "cand_id")

# Print the result
dim(result)

```

### Q3.4 Exploring - Indicator Variables and Scatter Plot

```{r}

#Create a new variable candidate_party to indicate whether each individual is a "Democrat", "Republican" or "Other Party" based on the party column.
result$candidate_party <- result$party
mask <- !(result$candidate_party=='REP' | result$candidate_party=='DEM')
result$candidate_party[mask] <- "OTHER"

unique(result$candidate_party)
```

```{r}
#Use ggplot to produce a scatter plot of general_votes on the y-axis and ttl_disb on the x-axis and color the points with the new candidate_party variable. Please do not transform the variables (log, sqrt, etc.) before plotting. 

plt <- result %>%  
  ggplot() + 
  aes(x = ttl_disb, y = general_votes, color=candidate_party) +
  geom_point(stat = "identity") +
  ggtitle("Scatter Plot of\nCampaign Contributions vs. Votes in the House\n")+
  labs(x = "Campaign Contributions ($)", y="House Votes")+
  scale_y_continuous(labels = scales::comma)+
  scale_x_continuous(labels = scales::comma)+
  theme(plot.title = element_text(hjust = 0.5))
  #+
  #scale_y_continuous(limits =  c(0, 100000))+
  #scale_x_continuous(limits =  c(0, 1000000))
plt
```

```{r}

model <- lm(general_votes ~ ttl_disb + candidate_party,data=result)
summary(model)
```

### Q3.5 Regression - Evaluate large sample assumptions

*Evaluate the large-sample linear model assumptions presenting evidence based on your background knowledge, visualizations, and numerical summaries. Please limit your answer for this subpart evaluating both assumptions to no more than a page in total. Written responses should be no longer than 5 sentences for each assumption.*

**Linearity**: Looking at the scatter plot above, the relationship appears to roughly have a positive linear relationship for REPUBLICAN and DEMOCRAT, however, the slopes by categories do appear different. The OTHER category has a much lower slope (potentially negative) for a large cluster of samples.

**Independence**: The residuals have clustered outcomes. So regression appears to have independ

```{r}
plt2 <- model %>%  
  ggplot() + 
  aes(y = model$residuals, x = model$fitted.values)+
  geom_point(stat = "identity") +
  ggtitle("Scatter Plot of\nCampaign Contributions vs. Votes in the House\n")+
  labs(x = "House Votes", y="Residuals") +
  scale_y_continuous(labels = scales::comma)+
  scale_x_continuous(labels = scales::comma)
plt2
```
