---
title: "HW9"
output: html_document
---

```{r setup, include=FALSE}
## install the package if it's not installed
## note: need to install libgit2-dev in terminal
##      >> apt-get update
##      >> apt-get install libgit2-dev
install.packages("remotes")
remotes::install_github("baumer-lab/fec16",force=TRUE)
# then select 1 for all updates
library(fec16)

library(ggplot2)
library(magrittr)
install.packages("gridExtra")
library(gridExtra)

install.packages('dplyr')
library(dplyr)

knitr::opts_chunk$set(echo = TRUE)
```

```{r}

result$candidate_party <- result$party
mask <- !(result$candidate_party=='REP' | result$candidate_party=='DEM')
result$candidate_party[mask] <- "OTHER"

unique(result$candidate_party)
```

```{r}

result %>%  
  ggplot() + 
  aes(x = ttl_disb, y = general_votes, color=candidate_party) +
  geom_point(stat = "identity") +
  ggtitle("Scatter Plot of\nCampaign Contributions vs. Votes in the House\n")+
  labs(x = "Campaign Contributions ($)", y="House Votes")+
  scale_y_continuous(labels = scales::comma)+
  scale_x_continuous(labels = scales::comma)+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(color = "Party")

```

```{r}

model <- lm(general_votes ~ ttl_disb + candidate_party,data=result)
summary(model)
```

### Q3.5 Regression - Evaluate large sample assumptions

*Evaluate the large-sample linear model assumptions presenting evidence based on your background knowledge, visualizations, and numerical summaries. Please limit your answer for this subpart evaluating both assumptions to no more than a page in total. Written responses should be no longer than 5 sentences for each assumption.*

**Linearity**: Looking at the scatter plot above, the relationship appears to roughly have a positive linear relationship for REPUBLICAN and DEMOCRAT, however, the slopes by categories do appear different. The OTHER category has a much lower slope (potentially negative) for a large cluster of samples.

**Independence**: The residuals have clustered outcomes. So regression appears to have independ

```{r}
plt2 <- model %>%  
  ggplot() + 
  aes(y = model$residuals, x = model$fitted.values)+
  geom_point(stat = "identity") +
  ggtitle("Scatter Plot of\nCampaign Contributions vs. Votes in the House\n")+
  labs(x = "House Votes", y="Residuals") +
  scale_y_continuous(labels = scales::comma)+
  scale_x_continuous(labels = scales::comma)
plt2
```
